---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snakemakeR

<!-- badges: start -->
<!-- badges: end -->

`snakemakeR` helps R-first analysts capture the small but repetitive step of
drafting a minimal Snakemake S4 scaffold. Instead of copying code between
projects, you can generate a vetted snippet or paste it directly into the
RStudio editor and immediately focus on the parts of the pipeline that matter.

## Why snakemakeR?

- Works entirely in R, making it easy to slot into existing scripts.
- Keeps the S4 class definition in one helper so fixes stay in sync.
- Provides both textual and RStudio editor helpers, depending on your workflow.

## Installation

You can install the development version of snakemakeR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("AmelZulji/snakemakeR")
```

## Usage

Retrieve the Snakemake S4 scaffold as a single string. This is handy when you
want to review or tweak the snippet before inserting it elsewhere, and you can
control how many placeholder entries are generated for each slot.

```{r pull-template, eval = TRUE}
library(snakemakeR)

cat(build_snakemake_s4_snippet(n_input = 2, n_output = 1, n_param = 1))
```

If you are working inside RStudio, you can paste the same scaffold directly into
the active source document at the cursor location.

```{r paste-template, eval = FALSE}
if (rstudioapi::isAvailable()) {
  insert_snakemake_s4_snippet(n_input = 2, n_output = 1, n_param = 1)
}
```

Both helpers call the same builder, so any adjustments to the snippet logic are
reflected across the package automatically.

## Template preview

Here is the default snippet shipped with the package:

``` r
setClass(
  "Snakemake",
  slots = list(
    input = "list",
    output = "list",
    params = "list"
  )
)

snakemake <- new(
  "Snakemake",
  input = list(
    input1 = ""
  ),
  output = list(
    output1 = ""
  ),
  params = list(
    param1 = ""
  )
)
```

## Development

- Run `devtools::load_all()` while iterating on the snippet builder to pick up changes.
- Execute `devtools::test()` (or `testthat::test_dir("tests/testthat")`) to
  ensure the generated snippet stays wired correctly.
- Render this README with `devtools::build_readme()` so `README.md` stays in
  sync with `README.Rmd`.
